Title Text

### 2014-04-06 paper.tex
please read email
please read my notes. I'll await your edits.

As an example of fusion consider the example
\verb!map (*2) (map (*5) arr)!, where each element of the array
\verb!arr! is first multiplied by five and then again by
two. Conceptually, there is an intermediate array created after the
first \verb!map! but thanks to fusion it will be removed. Fusion will proceed
as follows:

@@

The correctness of fusion relies crucially on the language being
\emph{pure}. If side effects where allowed in the indexing function
fusion would not be correct.

@@

Fusion effectively makes Pull arrays \emph{virtual} in that they will
not be represented in memory. All intermediate arrays will be
remove. But sometimes it is important to keep an array in memory, not
least to produce the final result. For this reason, Pull arrays
provide a function, variously known as \verb!force!, \verb!memorize!
  or \verb!store!. We will refer to it as \verb!store! here. The
  functional semantics of \verb!store! is the identity function,
  i.e. it simply returns the same array as it was given. However, as a
  side effect it stores the array to memory.

@@

An initial observation is that MoA and Pull arrays where developed for
different purposes and that can be seen already by looking at the
notation. Mathematics of arrays have first and foremost been used for
calculating array programs by hand. This is reflected in the short
names and succinct notation which works very well when doing
pencil-and-paper proofs.

Pull arrays on the other hand where conveived in the context of a
typed functional language. The notation is completely inherited from
the syntax of Haskell \cite{marlow2010haskell}.

@@

When it comes to types MoA keeps things very simple. There are two
types: arrays and scalars. Furthermore, scalars and singleton arrays
are identified.

>>>>

As an example of fusion consider the example
\newline
\verb!map (*2) (map (*5) arr)!, where each element of the array
\verb!arr! is first multiplied by five and then again by
two. Conceptually, there is an intermediate array created after the
first \verb!map! but thanks to fusion it will be removed. Fusion will proceed
as follows:

@@

The correctness of fusion relies crucially on the language being
\emph{pure}. If side effects were allowed in the indexing function
fusion would not be correct.

@@

Fusion effectively makes Pull arrays \emph{virtual} in that they will
not be represented in memory. All intermediate arrays will be
removed. But sometimes it is important to keep an array in memory, not
least to produce the final result. For this reason, Pull arrays
provide a function, variously known as \verb!force!, \verb!memorize!
  or \verb!store!. We will refer to it as \verb!store! here. The
  functional semantics of \verb!store! is the identity function,
  i.e. it simply returns the same array as it was given. However, as a
  side effect it stores the array to memory.

@@

An initial observation is that MoA and Pull arrays were developed for
different purposes and that can be seen already by looking at the
notation. Mathematics of Arrays has first and foremost been used for
calculating array programs by hand. This is reflected in the short
names and succinct notation which works very well when doing
pencil-and-paper proofs.

Pull arrays on the other hand were conveived in the context of a
typed functional language. The notation is completely inherited from
the syntax of Haskell \cite{marlow2010haskell}.

@@

When it comes to types MoA keeps things very simple. There are two
types: arrays and scalars. Furthermore, scalars and singleton arrays
are identified.
% scalars are arrays from an MoA and Psi Calculus perspective.
